### 2015-10-16 stuff/dirfields/DirFields.tex
...

    An simple choice for an initial condition is
    \begin{align}
      \pfl_{0} &= \frac{\exd x}{\left\|\exd x  \right\|}
    \end{align}
    because we can discretize \( \exd x \) on an edge \( e=\left[ v_{1} , v_{2} \right] \) by (stokes theorem)
    \begin{align}
      \left( \exd x \right)_{h}(e) = \left( v_{2} - v_{1} \right)\cdot\base^{x} = v_{2}^{x} - v_{1}^{x} 
    \end{align}
    independent in the parametrization of the surface.
    Hence, after normalizing, there are three defects with a positive charge on the three bulges and one defect with a negative charge on the saddle point.
    (That are the 4 positions, where the tangential space is orthogonal to \( \base^{x} \).)
    If needed, by rising the indices we get the surface gradient of the \( x \)-component
    \begin{align}
      \left( \exd x \right)^{\sharp} &= \nabla_{\M}x
                  = \left[g^{ij}_{C,r}\partial_{j}x(\theta,\phi)\right]^{i=\theta,\phi}
                  = \left( I - \frac{\nabla \varphi_{C,r}}{\left\| \nabla \varphi_{C,r} \right\|}
                        \otimes\frac{\nabla \varphi_{C,r}}{\left\| \nabla \varphi_{C,r} \right\|} \right)\base^{x}
    \end{align}
    For the normalizing procedure, it is also the Hodge dual initial solution to discretized (the rotation of the \( x \)-component).
    If the face \( f_{1}\succ e \) is right of the edge \( e \) and \( f_{2}\succ e \) located left, 
    so that \( \star e = [c(f_{1}),c(f_{2})] \) is the dual edge, than we can approximate
    \begin{align}
      \left( *\exd x \right)_{h}(e) &= -\frac{\left| e \right|}{\left| \star e \right|} \left( \exd x \right)(\star e)
                                     = -\frac{\left| e \right|}{\left| \star e \right|} \left( \left[c(f_{2})  \right]^{x} - \left[c(f_{1})  \right]^{x} \right)
    \end{align}
    With the discrete norm \eqref{eqPDNorm} of the PD-1-form, we obtain the initial PD-1-form on \( e \in \E \) by
    \begin{align}
      \PDpflhInit(e) = \frac{
                       \begin{bmatrix}
                          v_{2}^{x} - v_{1}^{x}\\
            -\frac{\left| e \right|}{\left| \star e \right|} \left( \left[c(f_{2})  \right]^{x} - \left[c(f_{1})  \right]^{x} \right)
                       \end{bmatrix}_{PD}
                    }{\sqrt{\frac{1}{\left| e \right|^{2}}\left(v_{2}^{x} - v_{1}^{x}  \right)^{2}
                                     +\frac{1}{\left| \star e \right|^{2}}\left( \left[c(f_{2})  \right]^{x} - \left[c(f_{1})  \right]^{x}\right)^{2} }}
    \end{align}
    See figure \ref{figNonic}.
    \begin{figure}
      \centering
      \includegraphics[width=.9\textwidth]{bilder/Nonic50p_1.png}
      \caption{Nonic Surface with shift factor \( C = 1 \) and proportion factor \( r = 0.5 \).
               The mesh is well-centered.
               Plotted is the Gauss curvature.
               The arrows show the covariant initial solution \( \p_{0} \) on some vertices.}
      \label{figNonic}
    \end{figure}

>>>>

    An simple choice for an initial condition is
    \begin{align}
      \pfl_{0} &= \frac{\exd x}{\left\|\exd x  \right\|}
    \end{align}
    because we can discretize \( \exd x \) on an edge \( e=\left[ v_{1} , v_{2} \right] \) by (stokes theorem)
    \begin{align}
      \left( \exd x \right)_{h}(e) = \left( v_{2} - v_{1} \right)\cdot\base^{x} = v_{2}^{x} - v_{1}^{x} 
    \end{align}
    independent in the parametrization of the surface.
    Hence, after normalizing, there are three defects with a positive charge on the three bulges and one defect with a negative charge on the saddle point.
    (That are the 4 positions, where the tangential space is orthogonal to \( \base^{x} \).)
    If needed, by rising the indices we get the surface gradient of the \( x \)-component
    \begin{align}
      \left( \exd x \right)^{\sharp} &= \nabla_{\M}x
                  = \left[g^{ij}_{C,r}\partial_{j}x(\theta,\phi)\right]^{i=\theta,\phi}
                  = \left( I - \frac{\nabla \varphi_{C,r}}{\left\| \nabla \varphi_{C,r} \right\|}
                        \otimes\frac{\nabla \varphi_{C,r}}{\left\| \nabla \varphi_{C,r} \right\|} \right)\base^{x}
    \end{align}
    For the normalizing procedure, it is also the Hodge dual initial solution to discretized (the rotation of the \( x \)-component).
    If the face \( f_{1}\succ e \) is right of the edge \( e \) and \( f_{2}\succ e \) located left, 
    so that \( \star e = [c(f_{1}),c(f_{2})] \) is the dual edge, than we can approximate
    \begin{align}
      \left( *\exd x \right)_{h}(e) &= -\frac{\left| e \right|}{\left| \star e \right|} \left( \exd x \right)(\star e)
                                     = -\frac{\left| e \right|}{\left| \star e \right|} \left( \left[c(f_{2})  \right]^{x} - \left[c(f_{1})  \right]^{x} \right)
    \end{align}
    With the discrete norm \eqref{eqPDNorm} of the PD-1-form, we obtain the initial PD-1-form on \( e \in \E \) by
    \begin{align}
      \PDpflhInit(e) = \frac{
                       \begin{bmatrix}
                          v_{2}^{x} - v_{1}^{x}\\
            -\frac{\left| e \right|}{\left| \star e \right|} \left( \left[c(f_{2})  \right]^{x} - \left[c(f_{1})  \right]^{x} \right)
                       \end{bmatrix}_{PD}
                    }{\sqrt{\frac{1}{\left| e \right|^{2}}\left(v_{2}^{x} - v_{1}^{x}  \right)^{2}
                                     +\frac{1}{\left| \star e \right|^{2}}\left( \left[c(f_{2})  \right]^{x} - \left[c(f_{1})  \right]^{x}\right)^{2} }}
    \end{align}
    See figure \ref{figNonic} for the covariant vector field \( \p_{0} \), well centered triangulation and Gauss curvature.
    \begin{figure}
      \centering
      \includegraphics[width=.9\textwidth]{bilder/Nonic50p_1.png}
      \caption{Nonic Surface with shift factor \( C = 1 \) and proportion factor \( r = 0.5 \).
               The mesh is well-centered.
               The Gauss curvature is plotted too.
               The arrows show the contravariant initial solution \( \p_{0} \) on some vertices.}
      \label{figNonic}
    \end{figure}

    The surface parameters \( r \) and \( C \) affect the geometric properties and hence the dynamic of the solution behavior and the final
    equilibrium state.
    To test the influence of these parameters, we choose a fixed proportion factor \( r=0.99 \).
    This is nearly the symmetric case \( r=1 \), but to choose \( r \) slightly less than one is to be enough to prevent metastable
    solutions.
    By variating of the shift factor \( C\in\left[ 0.96 , 1.00 \right] \) the system rises two fundamental different equilibrium solutions.
    If \( C < 0.98 \) then we always get a \( \left\{ + , + \right\} \) charge defect configuration
    (see figure \ref{figNonicCompare} (bottom)).
    If \( C \ge 0.98 \) then the final solution stay a \( \left\{ + , +, + , - \right\} \) configuration
    (see figure \ref{figNonicCompare} (top)).
    \begin{figure}
      \centering
      \includegraphics[width=.9\textwidth]{bilder/NonicCompareFinal.png}
      \caption{Nonic Surface (\( r=0.99 \)) with shift factor \( C = 1 \) (top row) and \( C = 0.96 \) (bottom row)
               with view in \( x \)-direction (right) and \( (-x) \)-direction (left).
               The final contravariant solutions \( \p_{\infty} \) and their norm are plotted for visualising the charge defects.
               In the top row arises two sinks, one source and one saddle point defects.
               In the bottom row we get finally only one sink and one source defects, which is slightly below the bulge (right). 
               }
      \label{figNonicCompare}
    \end{figure}
    We choose \( K_{n} = 800 \) in the discretized PDE to resolve sufficiently the defect radii.
    The Frank-Oseen-Energy and the time, when two of the four defects are fusing for \( C < 0.98 \), are plotted in figure
    \ref{figNonicExperiment}. 
    \begin{figure}
      \centering
      \includegraphics[width=.99\textwidth]{bilder/nonicExperiment.pdf}
      \caption{Parameter study for the shift factor \( C\in[0.96,1] \).
               Plotted are the final Frank-Oseen-Energy and the fusion time, when the shrink defect from the slightly minor bulge and the saddle
               point defect are fully self-neutralized.
               This only happens for \( C < 0.98 \). 
               In the left limes the fusion time becomes singularly.
               The energy increase only very weakly linear in \( C \) up to \( C \nearrow 0.98 \). 
               After the energy jump (transition from the 2-defects to the 4-defects configuration) the energy decrease also very weakly linear.
               }
      \label{figNonicExperiment}
    \end{figure}
